Self-assembly of colloid-cholesteric composites provides a possible route to switchable optical materials

### 2014-03-21 trunk/papers/2012-sandwich/support.tex
Second reply
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2351 40876441-3496-0410-a613-a2fca35b2ae2

The surface anchoring for colloids is as before: always normal, but with
$WR/K = 0.23$ and $WR/K = 2.3$. The colloid solid volume fractions are
1\% and 4\%.
\textcolor{red}{For both normal and planar anchoring at the walls,
the value of $W$ is the same as that used for the strongly anchoring
particles.}
All simulations are run for two million simulation time steps.

@@

To summarise, the simulations represent BP-forming materials, with the
interpretation of the simulation units for length, time, and energy
density being close to 10~nm, 10~ns, and 100~MPa respectively.
\textcolor{red}{For a Frank eleastic
constant of $K = 70$~pN and unit cell sizes in the range
$\lambda =$100--500~nm, a corresponding shear modulus $G \simeq
K/\lambda^2 =$0.3--7~kPa.}

@@

\bibitem{blue1}
Wright, D.C., and Mermin, N.D.,
Crystalline liquids: the blue phases,
{\it Rev. Mod. Phys.} {\bf 61,} 385-432 (1989).
\bibitem{oliver1}
Henrich, O., Marenduzzo, D., Stratford, K., and Cates, M.E.,
Thermodynamics of blue phases in electric fields,
\textit{Phys. Rev. E}, \textbf{81} 031706 (2010).
\bibitem{oliver-bp3}
Henrich, O., Stratford, K., Cates, M.E., and Marenduzzo, D.,
Structure of blue phase III of cholesteric liquid crystals,
{\it Phys. Rev. Lett.} {\bf 106}, 107802 (2011).
\bibitem{denniston2}
Denniston, C., Marenduzzo, D., Orlandini, E., and  Yeomans, J.M.,
Lattice Boltzmann algorithm for three-dimensional liquid-crystal
hydrodynamics,
\textit{Philos. Trans. R. Soc. London, Ser. A} \textbf{362}, 1745 (2004).
\bibitem{oliver2}
Henrich, O., Stratford, K.,  Marenduzzo, D., and Cates, M.E.,
Ordering dynamics of blue phases entails kinetic stabilization of
amorphous networks, 
\textit{Proc. Acad. Sci. USA} \textbf{107}, 1312 (2010).
\bibitem{denniston}
Denniston, C., Orlandini, E., and Yeomans, J.M.,
Lattice Boltzmann simulattions of liquid crystal hydrodynamics,
\textit{Phys. Rev. E} \textbf{63}, 056702 (2001).
\bibitem{deGennes}
\textcolor{red}{de Gennes, P.-G., and  Prost, J.,
{\it The Physics of Liquid Crystals} (Clarendon Press, 1995).}
%\bibitem{fournier2005}
%J.-B. Fournier and P. Galatola,
%\textit{Europhys. Lett.} \textbf{72}, 403 (2005).
\bibitem{codef} Cates, M.E.,  et al.,
Simulating colloid hydrodynamics with lattice Boltzmann,
\textit{J. Phys. Condens. Matter} \textbf{16},  3903 (2004).

>>>>

The surface anchoring for colloids is as before: always normal, but with
$WR/K = 0.23$ and $WR/K = 2.3$. The colloid solid volume fractions are
1\% and 4\%.
\textcolor{red}{For both normal and planar anchoring at the walls,
the strength is adjusted to correspond to that used for the strongly
anchoring particles.}
All simulations are run for two million simulation time steps.

@@

To summarise, the simulations represent BP-forming materials, with the
interpretation of the simulation units for length, time, and energy
density being close to 10~nm, 10~ns, and 100~MPa respectively.
For a Frank eleastic
constant of $K = 70$~pN and unit cell sizes in the range
$\lambda =$100--500~nm, a corresponding shear modulus $G \simeq
K/\lambda^2 =$0.3--7~kPa.

@@

\bibitem{blue1}
Wright, D.C., and Mermin, N.D.,
Crystalline liquids: the blue phases,
{\it Rev. Mod. Phys.} {\bf 61,} 385-432 (1989).
\bibitem{oliver1}
Henrich, O., Marenduzzo, D., Stratford, K., and Cates, M.E.,
Thermodynamics of blue phases in electric fields,
\textit{Phys. Rev. E}, \textbf{81} 031706 (2010).
\bibitem{oliver-bp3}
Henrich, O., Stratford, K., Cates, M.E., and Marenduzzo, D.,
Structure of blue phase III of cholesteric liquid crystals,
{\it Phys. Rev. Lett.} {\bf 106}, 107802 (2011).
\bibitem{denniston2}
Denniston, C., Marenduzzo, D., Orlandini, E., and  Yeomans, J.M.,
Lattice Boltzmann algorithm for three-dimensional liquid-crystal
hydrodynamics,
\textit{Philos. Trans. R. Soc. London, Ser. A} \textbf{362}, 1745 (2004).
\bibitem{oliver2}
Henrich, O., Stratford, K.,  Marenduzzo, D., and Cates, M.E.,
Ordering dynamics of blue phases entails kinetic stabilization of
amorphous networks, 
\textit{Proc. Acad. Sci. USA} \textbf{107}, 1312 (2010).
\bibitem{denniston}
Denniston, C., Orlandini, E., and Yeomans, J.M.,
Lattice Boltzmann simulattions of liquid crystal hydrodynamics,
\textit{Phys. Rev. E} \textbf{63}, 056702 (2001).
\bibitem{deGennes}
de Gennes, P.-G., and  Prost, J.,
{\it The Physics of Liquid Crystals} (Clarendon Press, 1995).
%\bibitem{fournier2005}
%J.-B. Fournier and P. Galatola,
%\textit{Europhys. Lett.} \textbf{72}, 403 (2005).
\bibitem{codef} Cates, M.E.,  et al.,
Simulating colloid hydrodynamics with lattice Boltzmann,
\textit{J. Phys. Condens. Matter} \textbf{16},  3903 (2004).
